### 2020-01-20 README.Rmd
Add a set_packageId() method
Package ID will now be set explicitly be a dedicated function, and *not set automagically* by write_eml().  write_* functions should not have unexpected side-effects that modify the output data!

```{r}
me <- list(individualName = list(givenName = "Carl", surName = "Boettiger"))
my_eml <- list(dataset = list(
              title = "A Minimal Valid EML Dataset",
              creator = me,
              contact = me)
            )

>>>>

```{r}
me <- list(individualName = list(givenName = "Carl", surName = "Boettiger"))
my_eml <- list(dataset = list(
              title = "A Minimal Valid EML Dataset",
              creator = me,
              contact = me)
            )
my_eml <- set_packageId(my_eml)
